DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

There are various mathematical representations for control 
systems,  e.g.,  transfer functions and state-space equations (difference or differential equations). 
Here, 
systems with a single input and a single output (SISO) are considered and 
represented by transfer functions or state-space LTI models. LTI models 
are used in several engineering applications to support non-trivial tasks when 
applied to embedded systems (e.g., robot manipulator, power plants 
and guidance system). The following expression presents the general form 
of a discrete plant or a digital controller based on the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called the backward-shift operator; $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials; and $N$ and $M$
represent the denominator and numerator polynomials order, respectively.
%
In a state-space form, 
the behavior of a system is represented via a state evolution equation $x(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

@@

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
program synthesis engines and considering the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.

The present paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 
lies on designing physical plants in MATLAB and then promptly synthesizing a stable and safe digital controller,
considering the complete range of approximations. 
Additionally, when using the \tool, an engineer is able to model a physical plant with MATLAB, 
through transfer-function or state-space representations, considering low-level systems parameters 
(implementation features and numerical format), and then to synthesize a stable and safe digital controller.

>>>>

There are various mathematical representations for control 
systems,  e.g.,  transfer functions and state-space equations (difference or differential equations). 
Here, 
systems with a single input and a single output (SISO) are considered and 
represented by transfer functions or state-space LTI models. LTI models 
are used in several engineering applications to support non-trivial tasks when 
applied to embedded \& cyber-physical systems (e.g., robot manipulator, smart grid, 
power plants, distributed robotics, and automatic pilot avionics). 
The following expression presents the general form 
of a discrete plant or a digital controller based on the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called the backward-shift operator; $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials; and $N$ and $M$
represent the denominator and numerator polynomials order, respectively.
%
In a state-space form, 
the behavior of a system is represented via a state evolution equation $x(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

@@

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox, but applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
program synthesis engines and considering the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.

The present tool paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 
lies on designing physical plants in MATLAB and then promptly synthesizing a stable and safe digital controller,
considering the complete range of approximations. 
Additionally, when using the \tool, an engineer is able to model a physical plant with MATLAB, 
through transfer-function or state-space representations, considering low-level systems parameters 
(implementation features and numerical format), and then to synthesize a stable and safe digital controller.
